---
title: "Presentación con Slidy de Rmarkdown"
author: "Alberto Rodríguez R"
date: "31 de diciembre de 2017"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Diapositiva Incremental

* Paso 1
* Paso 2
* Paso 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Bullets

```{r pressure}
plot(pressure)
```

## Gráfico con Ggplot2

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
ggplot(data = iris, aes(x = Sepal.Width, y = Petal.Width, shape = Species, color = Species)) + geom_point(size = 4)
```

## Mapa interactivo con Leaflet

```{r out.width='100%', warning=FALSE, fig.height=5, eval=require('leaflet'), echo=FALSE}
library(leaflet)
leaflet() %>% addTiles() %>% setView(-74.0841, 4.63858, zoom = 16)
```

